A review on Generative Learning in Computer Vision

### 2020-05-08 paper.tex
added abstract

\begin{abstract}

\end{abstract}

@@

The rest of the paper is organized as follows-- Section \ref{lr} will provide an overview of generative learning. Section \ref{techniques} will cover recent techniques used for generative learning. Section \ref{comparison} will provide a comparison of different techniques discussed in section \ref{techniques}. Finally, section \ref{conclusion} will provide some remarks to conclude the paper.

@@

\section{Comparison}
\label{comparison}

>>>>

\begin{abstract}
Generative learning is the technique to generate artificial data. This paper has covered a brief review of different generative learning techniques applied in computer vision to generate visual data. With advancement in computing power especially utilisation of GPU for distributed computing, a lot of deep learning techniques has been developed in this field of computer vision. Generative Adversarial Networks and autoencoders are such unsupervised deep learning neural networks. GANs have garnered a lot of interest by computre scientists due to its high quality image generation and also because of its novel yet simple architecture. A lot of variants of GANs are have been developed since the original GAN was introduced by Goodfellow et al in 2014 \cite{b1}. These variants have either tweak or have build upon the existing model. Some of the techniques covered in this paper are conditional GAN, progressive GAN, deep convolutional GANs, auxiliary GAN, InfoGANs, 3D-GAN, PacGAN, Pix2PixGAN, Cycle-GAN, Text-to-Image Synthesis (StackGAN), and Super-Resolution GAN. These models are just a few among others presented by researchers. This paper has also provided a brief critique on Variational Autoencoders which is a variant of the autencoder neural network. 
\end{abstract}

@@

The rest of the paper is organized as follows-- Section \ref{lr} will provide an overview of generative learning. Section \ref{techniques} will cover recent techniques used for generative learning. Finally, section \ref{conclusion} will provide some remarks to conclude the paper.

@@
